\begin{problem}{The spell}{standard input}{standard output}{1 second}{256 megabytes}

These Days, As you know $Mazen$ doesn't have time to make creative problems so he will give you this easy task.

Initially, you have the number $1$ and you asked to get the number $n$ using these two spells:
\begin{enumerate}
  \item Assume you have number $x$ now. If you use the first spell, then number $x$
 becomes $2x+1$.
  \item Assume you have number $x$ now. If you use the second spell, then number $x$
 becomes $2x$.
\end{enumerate}
Construct a sequence of spells, so you get the number $n$ after using them in order.

\InputFile
The first line contains a single integer $t$ $(1≤t≤10^4)$ --- the number of test cases.

Each test case contains one line with a single integer $n$ $(2≤n≤10^9)$ --- the required final number.

\OutputFile
For each test case, output the following.

In the first line print an integer $m$ representing the total number of spells you use.
In the second print $m$ integers $a_1,a_2,\ldots,a_m$
 ($a_i$ is $1$ or $2$) separated by spaces, where $a_i=1$
 means that you use the first spell in the $i$
-th step, while $a_i=2$
 means that you use the second spell in the $i$
-th step.

\Example

\begin{example}
\exmpfile{example.01}{example.01.a}%
\end{example}

\Note
For the first test case initially, you have the number $1$ first you can use the second spell
as follow $2 \times 1 = 2$ you get $2$ and use the first spell as follow $2 \times 2 + 1 = 5$ you get the required number.

\end{problem}

