\begin{problem}{Marei El Brimo}{standard input}{standard output}{1 second}{256 megabytes}

$Marei$ is a watermelon seller. So he will sell $n$ different watermelons with prices $a_i$ for all $i$ $(1 \le i \le n)$.




and there are $q$ customers who come to buy from him.




Each customer will buy $j_{th}$  watermelon $j:(1\le j\le n)$, You should tell this customer what is the price he will buy his watermelon from $Marei$.

Each customer will also come with two integers $x$ and $y$ recommend $Marei$ to change $x_{th}$ watermelon's price with price $y$. As you know, $Marei$ is a greedy seller, so he can take the customer's recommended price or not.

After that, you need to tell me the amount of money that $Marei$ will earn from his customers.

$NOTE:$ The customer will buy first and then recommend changing another watermelon's price.

suppose for each different watermelon you have an infinite supply of it.

\InputFile
First line contains $n-(1 \le n \le 2 \cdot 10^5)$- number of watermelons.

Second line contains n integers-$(1\le a_i \le 10^9)$ for all $i-(1\le i\le n)$ price for each watermelon.

Third line contains $q-(1 \le q \le 2 \cdot 10^5)$- number of customers.

For each customer, there are $j,x,y-(1\le j,x \le n),(1\le y \le 10^9)$

$j$ is the watermelon the customer will buy, $x$ is the watermelon the customer recommends changing its price and $y$ is the new price recommended for it.

\OutputFile
For each line, you should tell the customer the price of his watermelon.

And in the last line, you should tell me the amount of money that $Marei$ will earn from his customers.

\Example

\begin{example}
\exmpfile{example.01}{example.01.a}%
\end{example}

\Note
$The$ $first$ customer came to buy $ the$  $first$ watermelon for $10$ and recommended Marei change $the$  $second$ one's price to $15$ Marei is greedy, So he will change the $second$ one's price to $max(15,4)$


$The$ $second$ customer came to buy $the$  $second$ one so he found that $the$ 
 $second$ one's price is $15$ and recommended changing $the$ $first$ one's price to $4$ but Marei will take $max(10,4)$.

and so on.

\end{problem}

