\begin{problem}{Tasks Day}{standard input}{standard output}{1 second}{256 megabytes}

Every weekend, $Mazen$ makes a day called $Tasks$ $Day$.

On this day, $Mazen$ gives his friends a number of tasks to solve.
$Mazen$ has an assistant that collects the progress of solving tasks in the form of
\begin{tabular}{ll}
  \bf{friend's name}&\bf{task name}& &  \bf{time taken to solve}\\
\end{tabular}
example:   
\begin{tabular}{ll}
  \bf{Hamza}&\bf{A}& &  \bf{40}\\
\end{tabular}

After collecting the list, $Mazen$ comes to see it, but he becomes angry because he needs it to be sorted as follows:

First, sort by the number of solved tasks, the friend with the greater number comes first.

If two friends have an equal number of solved tasks then the friend with less \huge{total} time taken to solve comes first. 

If two friends have an equal number of solved tasks and total time taken then the friend with the lexicographical smaller name comes first.

can you help the assistant to sort the list.

\InputFile
The first line contains $n$ -- $(1\le n \le 10^5)$~-- the number of items in the list. 

next $n$ line contains item details as follows:
\begin{tabular}{ll}
  \bf{friend's name}&\bf{task name}& &  \bf{time taken to solve}\\
\end{tabular}

Friend name will be a string that has at most $10$ upper and lower case English letters.

task name will be an uppercase English character.

time taken in minutes $(1\le time \le 3000)$.


\OutputFile
output the list after sorting it in the form of
\begin{tabular}{ll}
  \bf{friend's name}&\bf{number of solved tasks}& &  \bf{total time taken to solve}\\
\end{tabular}


\Example

\begin{example}
\exmpfile{example.01}{example.01.a}%
\end{example}

\Note
$Hamza$ comes first because he solved 3 tasks and $Islam$ second because he solved 2 tasks. but you can see $Mohamed$, $Mahmoud$ and $Mazen$ have the same number of solved tasks but $Mohamed$ comes first because he has the least total time taken to solve after that $Mahmoud$ and $Mazen$ have the same number of solved tasks, and same total time but $Mahmoud$ comes first because his name is lexicographically smaller than $Mazen$. 

\end{problem}

